Leadership across cultures and contexts

### 2019-11-03 leadership_across_cultures_contexts.Rmd

We evaluate the cross-cultural frequency in the functions and qualities of leaders and the costs and benefits of leadership for both leaders and followers using an ethnographic database previously built and published (doi.org/10.5281/zenodo.2541999), from which @garfield_evolutionary_2019 "tested" three theoretical models against the ethnographic record. Whereas @garfield_evolutionary_2019, documented supporting evidence in reference to influential theoretical models, our goals here are to let the ethnographic record speak for itself in understanding variation in the dimensions of leadership we are interested in, i.e., our methods and analyses are exploratory and not tricly theoretically driven.

@@

Coding operationalizations of the costs and benefits of leadership were eveloped *a priori* based on our reading of the evolutionary theoretical literature from anthropology and biology. For both followers and leaders, we code if there is evidence of costs or benefits in the following categories: social status/reputation, reduced or increased risk of harm or conflict, social services, territory, mating, fitness, food resources, other resources, and other costs or benefits not captured by these categories. See Table X.

>>>>

We evaluate the cross-cultural frequency in the functions and qualities of leaders and the costs and benefits of leadership for both leaders and followers using an ethnographic database previously built and published (doi.org/10.5281/zenodo.2541999), from which @garfield_evolutionary_2019 "tested" three theoretical models against the ethnographic record. Whereas @garfield_evolutionary_2019, documented supporting evidence in reference to influential theoretical models, our goals here are to let the ethnographic record speak for itself in understanding variation in the dimensions of leadership we are interested in, i.e., our methods and analyses are exploratory and not strictly theoretically driven.

@@

Coding operationalizations of the costs and benefits of leadership were developed *a priori* based on our reading of the evolutionary theoretical literature from anthropology and biology. For both followers and leaders, we code if there is evidence of costs or benefits in the following categories: social status/reputation, reduced or increased risk of harm or conflict, social services, territory, mating, fitness, food resources, other resources, and other costs or benefits not captured by these categories. See Table X.
